---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r description}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "FADvisor",
    Description = "This R package provides a suite of functions designed to generate key indicators for Fish Aggregating Devices (FADs). It simplifies the process of analyzing FAD-related data, offering insights into their usage, environmental impact, and overall performance. Ideal for researchers and environmentalists focused on sustainable fishing practices.",
    `Authors@R` = c(
      person("Taha", "Imzilen", email = "imzilen.taha@gmail.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0001-8257-9113"))
    )
  )
)
# Define License with use_*_license()
usethis::use_gpl_license(version = 3, include_future = TRUE)
```

# All-in-one function to deploy publicly on GitHub

Either use this GitHub all-in-one function or choose the steps one-by-one in the following sections.
See `vignette("share-on-a-github-website", package = "fusen")` for more information.

```{r, eval=FALSE}
# _All-in-one share of your package and its documentation on GitHub
fusen::init_share_on_github()
```


# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
# Use main for primary branch
usethis::git_default_branch_rename()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
remotes::install_local()
# README
usethis::use_readme_rmd()
# Code of Conduct
usethis::use_code_of_conduct("contact@fake.com")
# NEWS
usethis::use_news_md()
# Package structure (add this in a dev/Readme.md file)
fusen::draw_package_structure()
```

**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# Pipe
usethis::use_pipe()

# package-level documentation
usethis::use_package_doc()

# GitHub
# Add your credentials for GitHub
usethis::create_github_token()
gitcreds::gitcreds_set()

# _Or one step at a time
# Send your project to a new GitHub project (included in `init_share_on_github()`)
usethis::use_github()

# Set Continuous Integration
# _GitHub (included in `init_share_on_github()`)
usethis::use_github_action_check_standard()
usethis::use_github_action("pkgdown")
usethis::use_github_action("test-coverage")
# _GitLab
gitlabr::use_gitlab_ci(type = "check-coverage-pkgdown")
```

## Use everytime needed

```{r, eval=FALSE}
# Simulate package installation
pkgload::load_all()

# Generate documentation and deal with dependencies
attachment::att_amend_desc()

# Check the package
devtools::check()

# Add a new flat template
fusen::add_flat_template("add")
```

# Share the package

```{r, eval=FALSE}
# set and try pkgdown documentation website locally
usethis::use_pkgdown()
pkgdown::build_site()

# build the tar.gz with vignettes to share with others
devtools::build(vignettes = TRUE)

# Share your package and its documentation on GitHub
# usethis::create_github_token()
# gitcreds::gitcreds_set()
fusen::init_share_on_github()
```

